---
title: "CheeseProject"
author: "kitoh"
date: "2024-08-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# library
library(dplyr)
library(ggplot2)
library(cowplot)

```

## Dataset
We love cheeses and selected following;
```{r cheeses}
cheeses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-06-04/cheeses.csv')
cheeses <- cheeses[-which(is.na(cheeses$fat_content)),] # removed rows which do not contain fat content 

```
- What is the relationship between milk and fat content, flavor?   
- Which countries do produce the cheeses?

## Milks used to make cheeses


## Fat Ratio and milk

In this dataset, fat concent is a little bit messy
```{r pressure, echo=T}
unique(cheeses$fat_content)[1:10]
```
Therefore I set a function which converts them into "double"

```{r fat concent cleaning}
fatcont_func <- function(value){
  
  if(sub("%", "", value) == value){
    fatpar <- sub(" g.+", "", value) %>% as.double()
    
  }else if(sub("-", "", value) == value){
    fatpar <- sub("%", "", value) %>% as.numeric()
    
  }else{
    min <- sub("-.+", "", value) %>% as.integer()
    max <- sub(".+-", "", value) %>% sub("%", "", .) %>% as.integer()
    fatpar <- mean(min, max)
  }
  return(fatpar)
}

fat_content_cleaned <- c()
for (i in cheeses$fat_content){
 
  fat_content_cleaned <- c(fat_content_cleaned, fatcont_func(i))
  
}
cheeses$fat_content_cleaned <- fat_content_cleaned

```
Checking the result
```{r check cleaned fat content, echo=T}
head(fat_content_cleaned)
typeof(fat_content_cleaned)

```

Then, fat ratio of each milk cheeses was visualized.
```{r plot three milk, echo=T}
cheeses %>% 
  filter(., milk %in% c("cow", "goat", "sheep")) %>% 
  group_by(., milk) %>% 
  summarise(mean_fat = mean(fat_content_cleaned), 
            sd_fat = sd(fat_content_cleaned)) %>% 
  ggplot(., aes(x = milk, y = mean_fat, 
                ymin = mean_fat - sd_fat, ymax = mean_fat + sd_fat, 
                group = milk)) +
  geom_bar(stat = "identity", fill = c("cow" = "gray9", "goat" = "brown", "sheep" = "yellow")) + geom_errorbar(width = 0.5) +
  theme_cowplot(18) +
  xlab("") +
  ylab("Mean fat ratio [%]") +
  labs(title = "Fat Ratio of cheeses")
```

## Fat Ratio and milk - combination of milk
What happens when the milks are combined?
```{r plot five milk, echo=T}
cheeses %>% 
  filter(., milk %in% c("cow", "goat", "sheep", "cow, goat", "cow, sheep")) %>% 
  group_by(., milk) %>% 
  summarise(mean_fat = mean(fat_content_cleaned), sd_fat = sd(fat_content_cleaned)) %>% 
  ggplot(., aes(x = milk, y = mean_fat, 
                ymin = mean_fat - sd_fat, ymax = mean_fat + sd_fat, group = milk, fill = milk)) +
  geom_bar(stat = "identity", fill = c("cow" = "gray9", "cow, goat" = "tomato", "cow, sheep" = "firebrick3", "goat" = "brown", "sheep" = "yellow" )) +
  geom_errorbar(width = 0.5) +
  theme_cowplot(18) +
  xlab("") +
  ylab("Mean fat ratio [%]") +
  labs(title = "Fat Ratio of cheeses")
```

## Short summary 1 - fat of cheeses
#### Sheep: high fat   
#### cow: middle   
#### goat: low fat


