---
title: "CheeseProject"
author: "kitoh"
date: "2024-08-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# library
library(dplyr)
library(ggplot2)
library(cowplot)

```

## Dataset
We love cheeses and selected following;
```{r cheeses}
cheeses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-06-04/cheeses.csv')
cheeses <- cheeses[-which(is.na(cheeses$fat_content)),] # removed rows which do not contain fat content 

```
- What is the relationship between milk and fat content, flavor?   
- Which countries do produce the cheeses?

## Milks used to make cheeses


## Fat Ratio and milk

In this dataset, fat concent is a little bit messy
```{r pressure, echo=T}
unique(cheeses$fat_content)[1:10]
```
Therefore I set a function which converts them into "double"

```{r fat concent cleaning}
fatcont_func <- function(value){
  
  if(sub("%", "", value) == value){
    fatpar <- sub(" g.+", "", value) %>% as.double()
    
  }else if(sub("-", "", value) == value){
    fatpar <- sub("%", "", value) %>% as.numeric()
    
  }else{
    min <- sub("-.+", "", value) %>% as.integer()
    max <- sub(".+-", "", value) %>% sub("%", "", .) %>% as.integer()
    fatpar <- mean(min, max)
  }
  return(fatpar)
}

fat_content_cleaned <- c()
for (i in cheeses$fat_content){
 
  fat_content_cleaned <- c(fat_content_cleaned, fatcont_func(i))
  
}
cheeses$fat_content_cleaned <- fat_content_cleaned

```
Checking the result
```{r check cleaned fat content, echo=T}
head(fat_content_cleaned)
typeof(fat_content_cleaned)

```

Then, fat ratio of each milk cheeses was visualized.
```{r plot three milk, echo=T}
cheeses %>% 
  filter(., milk %in% c("cow", "goat", "sheep")) %>% 
  group_by(., milk) %>% 
  summarise(mean_fat = mean(fat_content_cleaned), 
            sd_fat = sd(fat_content_cleaned)) %>% 
  ggplot(., aes(x = milk, y = mean_fat, 
                ymin = mean_fat - sd_fat, ymax = mean_fat + sd_fat, 
                group = milk)) +
  geom_bar(stat = "identity", fill = c("cow" = "gray9", "goat" = "brown", "sheep" = "yellow")) + geom_errorbar(width = 0.5) +
  theme_cowplot(18) +
  xlab("") +
  ylab("Mean fat ratio [%]") +
  labs(title = "Fat Ratio of cheeses")
```

## Fat Ratio and milk - combination of milk
What happens when the milks are combined?
```{r plot five milk, echo=T}
cheeses %>% 
  filter(., milk %in% c("cow", "goat", "sheep", "cow, goat", "cow, sheep")) %>% 
  group_by(., milk) %>% 
  summarise(mean_fat = mean(fat_content_cleaned), sd_fat = sd(fat_content_cleaned)) %>% 
  ggplot(., aes(x = milk, y = mean_fat, 
                ymin = mean_fat - sd_fat, ymax = mean_fat + sd_fat, group = milk, fill = milk)) +
  geom_bar(stat = "identity", fill = c("cow" = "gray9", "cow, goat" = "tomato", "cow, sheep" = "firebrick3", "goat" = "brown", "sheep" = "yellow" )) +
  geom_errorbar(width = 0.5) +
  theme_cowplot(18) +
  xlab("") +
  ylab("Mean fat ratio [%]") +
  labs(title = "Fat Ratio of cheeses")
```

## Short summary 1 - fat of cheeses
#### Sheep: high fat   
#### cow: middle   
#### goat: low fat

#########################################

# Code for creating stack bar plots of distributions of animal, flavor, and aroma
# In addition, it creates distribution of flavor and aroma by dairy animals

#########################################
library(dplyr)
library(ggplot2)
library(stringr)
library(plotly)
library(tidyr)

cheeses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-06-04/cheeses.csv')
milk <- unique(cheeses$milk)

# Identify the number of NA

sum(is.na(cheeses$fat_content))
sum(is.na(cheeses$calcium_content))
sum(is.na(cheeses$flavor))
sum(is.na(cheeses$aroma))

# Subset data
AF <- cheeses[,c('flavor','aroma','milk')]

# Count the number of unique flavor and aroma in the data frame
AF %>% str_count(flavor)
AF %>% count(aroma)


#Split characters in flavor  - > This did not work
#stringr::str_split_1(AF$flavor)        
# lapply(AF$flavor, function(str) {
#   if (is.na(str)) NA else stringr::str_split_1(str, pattern = ", ")
# } )

# Make a series of small functions to separate multiple variables divided by ,
split_comma <- function(var) { 
  lapply(var, function(str) {
    if (is.na(str)) NA_character_ else stringr::str_split_1(str, pattern = ", ")
  })
}

unnest_split_comma <- function(df, var){
  df[[var]] <- split_comma(df[[var]])
  tidyr::unnest_longer(df, all_of(var)) 
}

AF %>% 
  unnest_split_comma("flavor") %>% 
  unnest_split_comma("aroma") %>% 
  unnest_split_comma("milk")

multi_unnest_split_comma <- function(df, vars){
  for (var in vars) {
    df <- unnest_split_comma(df, var)
  }
  df
}
split_df <- multi_unnest_split_comma(AF, c("flavor", "aroma","milk"))


# Count the occurrence of milk, flavor, aroma
milk_counts <- split_df %>%
  filter(!is.na(milk)) %>% 
  count(milk)

aroma_counts <- split_df %>%
  filter(!is.na(aroma)) %>% 
  count(aroma)

flavor_counts <- split_df %>%
  filter(!is.na(flavor)) %>% 
  count(flavor)

# Add percentage columns for the plots
total_count_milk <- sum(milk_counts$n)
total_count_aroma <- sum(aroma_counts$n)
total_count_flavor <- sum(flavor_counts$n)

# Milk
milk_counts <- milk_counts %>%
  mutate(percentage = (n / total_count_milk) * 100) %>% 
  mutate(milk = factor(milk, levels = milk[order(percentage, decreasing = TRUE)]))

milk_labels <- milk_counts %>%
  group_by(milk) %>%
  summarise(total_percentage = sum(percentage)) %>%
  mutate(label = paste0(milk, " (", round(total_percentage,1), "%)"))

milk_counts2 <- milk_counts %>%
  left_join(milk_labels, by = "milk") %>% 
  mutate(label = factor(label, levels = label[order(percentage, decreasing = TRUE)]))


# Aroma
aroma_counts <- aroma_counts %>%
  mutate(percentage = (n / total_count_aroma) * 100) %>% 
  mutate(aroma = factor(aroma, levels = aroma[order(percentage, decreasing = TRUE)]))

aroma_labels <- aroma_counts %>%
  group_by(aroma) %>%
  summarise(total_percentage = sum(percentage)) %>%
  mutate(label = paste0(aroma, " (", round(total_percentage,1), "%)"))

aroma_counts2 <- aroma_counts %>%
  left_join(aroma_labels, by = "aroma") %>% 
  mutate(label = factor(label, levels = label[order(percentage, decreasing = TRUE)]))



# flavor
flavor_counts <- flavor_counts %>%
  mutate(percentage = (n / total_count_flavor) * 100) %>% 
  mutate(flavor = factor(flavor, levels = flavor[order(percentage, decreasing = TRUE)]))

flavor_labels <- flavor_counts %>%
  group_by(flavor) %>%
  summarise(total_percentage = sum(percentage)) %>%
  mutate(label = paste0(flavor, " (", round(total_percentage,1), "%)"))

flavor_counts2 <- flavor_counts %>%
  left_join(flavor_labels, by = "flavor") %>% 
  mutate(label = factor(label, levels = label[order(percentage, decreasing = TRUE)]))




# Create bar stack plots
ggplot(milk_counts2, aes(fill=label, y=percentage, x="")) +  # plot for Milk
  geom_bar(position="fill", stat="identity") +  labs(
    title = "Percentage Distribution of dairy animals",
    x = "Dairy animals",  # Change as needed
    y = "Percentage", # Change as needed
    fill = "Dairy animals" # Legend title
  ) +
  theme_minimal() 

ggplot(aroma_counts2, aes(fill=label, y=percentage, x="")) +  # plot for aroma
  geom_bar(position="fill", stat="identity") +  labs(
    title = "Distribution of cheese aroma",
    x = "aroma",  # Change as needed
    y = "Percentage", # Change as needed
    fill = "Dairy animals" # Legend title
  ) +
  theme_minimal()

ggplot(flavor_counts2, aes(fill=label, y=percentage, x="")) +  # plot for flavor
  geom_bar(position="fill", stat="identity") +  labs(
    title = "Distribution of cheese flavor",
    x = "flavor",  # Change as needed
    y = "Percentage", # Change as needed
    fill = "Dairy animals" # Legend title
  ) +
  theme_minimal()

# Count the number of flavor and aroma by grouping milk
milk_group <- split_df %>%
  group_by(milk) %>%
  filter(!is.na(milk)) %>% 
  summarise(across(everything(), ~ n_distinct(., na.rm = TRUE))) %>% 
  mutate(milk = factor(milk, levels = milk[order(flavor, decreasing = TRUE)])) %>% 
  pivot_longer(!milk, names_to = "result", values_to = "count")

# Create grouped bar chart
ggplot(data = milk_group, aes(x = result, y = count, fill = milk)) +
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.75)  + theme_minimal() + 
  labs(
    title = "Distribution of flavor and aroma by dairy animals",
    x = "Types",  # Change as needed
    y = "Frequency", # Change as needed
  )
#########################################

# END

#########################################


